Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-10 ms.tex
assessing stripe vs window when the apertures are more than 512 px away horizontally

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode Time Series}
\fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:stripeVsWindowAZlab04}
\end{figure*}

>>>>

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode Time Series}
\fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier), but the overall trends are similar.
}\label{fig:stripeVsWindowAZlab04}
\end{figure*}

The window mode does have the benefit of only using one amplifier.
This means that 1/f noise can be subtracted along rows whereas in stripe mode, 1/f noise has to be subtracted an an amplifier by amplifier basis (within 512 wide amplifier regions).
The trade-off is that there are 4 times fewer frames per second.
We assess the relative value of the 1/f correction versus different reads by placing the source aperture horizontally more than 512 pixels from the background aperture.
For stripe mode, this means that the apertures are on different amplifiers.
For window mode, this means the apertures are on the same amplifier.
